%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Alex} % Your first name
\familyname{Ledger} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Resume}
\address{7827 SE 35th Ave}{Portland, OR 97202}

\mobile{(417) 766 9854}
\email{a.led1027@gmail.com}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{Interested in ...}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

%\section{Personal Statement}
%\cvitem{}{Climate Change is perhaps the biggest problem of our generation, and we need to start innovating. I want to tackle climate change using my background in Math, Computer Science and Machine Learning, so that we can start innovating and adapting for the future.}

\section{Education}

\cventry{2012--Present}{Bachelor of Arts in Math-Computer Science}{}{\textit{Reed College} (in progress)}{}{}  

\section{Undergraduate Thesis}

\cvitem{Topic}{\emph{Improving Methods for Secure Computation (in progress)}}
\cvitem{Field}{Cryptography}
\cvitem{Advisor}{Professor Adam Groce}
\cvitem{Description}{Explores methods of secure computation, a cryptographic protocol for allowing two people who do not trust each other to work together. I implement new, faster methods of secure computation in C and achieve an order of magnitude speed up over prior work.}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\subsection{Research}

\cventry{2015--Present}{Math-Computer Science Research Assistant}{Reed College}{Portland}{}{
\begin{itemize}
    \item Worked with professor Adam Groce on Oblivious RAM (ORAM), a subfield of cryptography focused on obfuscating a client's access patterns to a server. 
    \item Implemented old and new ORAM protocols in C++, wrote cryptographic proofs that the protocols were secure, and in the process of writing a paper.
\end{itemize}
}

\cventry{2016--Present}{Computational Biology Research Assistant}{Reed College}{Portland}{}{
\begin{itemize}
    \item Worked with professor Anna Ritz on genomic analysis.
    \item Statistically analyzed genome mapping algorithms and developed methods for detecting and characterizing structual variants.
\end{itemize}
}
\cventry{2015--Present}{Artificial Life Lab Research Assistant}{\textit{Reed College}}{Portland}{}{
\begin{itemize}
    \item Worked with professor Mark Bedau on examining whether culture and technology exhibits aspects of evolution, using U.S. patents as a proxy for "technology in culture". 
    \item Employed many statistical and machine learning techniques to analyze the patents database including neural nets, natural language processing techniques, regression models, anomaly detection algorithms, and other network algorithms. 
\end{itemize}
}

\subsection{Industry}

\cventry{2014}{Software Engineering Intern}{\textit{The Program PDX}}{Portland}{}{Used  C++, OpenFrameworks and video technologies such as the Microsoft Kinect and webcams to construct engaging applications for children's museums and retail stores}

\cventry{2014-2015}{Webmaster of Reed Student Body Website}{\textit{Reed College}}{Portland}{}{Administered a LAMP server and maintained and built Python-Django web applications for the Reed College student body website.}

\cventry{2014-2015}{Teaching Assistant}{\textit{Reed College}}{Portland}{}{Teaching Assistant for Math 121, Reed's introduction to computer science course.}

\section{Skills}
\cvitem{Experienced}{Python, C, C++, Java, Latex, R, Bash, MongoDB, NoSQL }
\cvitem{Experienced}{Linux, Git version control, Subversion, HTML, Haskell}
\cvitem{Intermediate}{Scala, SQL, Ruby, Javascript, Clojure, Mathematica, Matlab}

\section{Coursework}
\cvlistdoubleitem{Computer Systems}{Cryptography}
\cvlistdoubleitem{Algorithms and Data Structures}{Probability}
\cvlistdoubleitem{Computability and Complexity}{Abstract Algebra}
\cvlistdoubleitem{Real Analaysis}{Linear Algebra}
\cvlistdoubleitem{Multivariable Calculus}{2 years of Physics}
\cvlistdoubleitem{2 years of Economics}{}

\section{More Information}
\cvitem{Github}{github.com/aled1027}
\cvitem{LinkedIn}{linkedin.com/pub/alex-ledger/61/ab4/75a}

\section{Other Interests}
\cvlistitem{Cryptography}
\cvlistitem{Machine Learning}
\cvlistitem{Climate Change}
\cvlistitem{Artificial Intelligence}
\cvlistitem{Network and Graph Theory}
\cvlistitem{Dynamical Systems and Chaos Theory}
\cvlistitem{Internet of Things}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
%\section{Awards}
%\cvitem{2011}{School of Business Postgraduate Scholarship}
%\cvitem{2010}{Top Achiever Award -- Commerce}

%\section{Interests}
%\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
%\cvlistdoubleitem{Piano}{Chess}
%\cvlistdoubleitem{Cooking}{Dancing}
%\cvlistitem{Running}
%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------
% To remove the cover letter, comment out this entire block
%\clearpage
%\recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
%\makelettertitle % Print letter title
%\lipsum[1-3] % Dummy text
%\makeletterclosing % Print letter signature
%----------------------------------------------------------------------------------------

\end{document}
